The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-16 src/ms.tex
fix ROSES grant number

\subsubsection{Data Central and the Anglo-Australian Telescope Archive}
\secauthor{James Tocknell}
Data Central is one of the five Australian Virtual Observatory\footnote{known as
  the All-Sky Virtual Observatory, or ASVO} nodes, providing both Australian and
international astronomers access to and services for surveys of the southern
sky. Whilst primarily hosting optical data, including the Anglo-Australian
Telescope (AAT) Archive\footnote{The AAT Archive is currently jointly managed by
  Data Central, Astronomy Australia Limited (AAL), and National Computational
  Infrastructure (NCI)}, Data Central also assists theoretical and radio
astronomers host and manage their data.

Python is widely used by Data Central, and \astropy and its wider ecosystem play
a vital role in the initial ingestion, reduction, access and visualisation of
the hosted data and services. For example, the AAT Archive hosts data back to
1974, so \astropycoordinates, \astropytime and \astropyfits are used to ingest
data flowing from the AAT to ensure that a consistent time and coordinate
system is provided to users for simpler querying.

As many of the surveys hosted by Data Central are spectroscopic surveys from the
AAT, specutils is heavily used to standardise the variety of encodings of
spectroscopic data into a form easily readable and visualisable by many standard
tools (such as ds9 or splat). Data Central has upstreamed into specutils loaders
for all hosted spectra, including 2dfdr-reduced spectra from the AAT Archive,
and strongly encourages other archives to provide loaders for their data to
further reuse of existing archival data.

@@

The \astropy community is supported by and makes use of a number of
organizations and services outside the traditional academic community.
We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors.
We also thank NumFOCUS and the Python Software Foundation for financial
support.
Within the academic community, we thank institutions that make it possible that
astronomers and other developers on their staff can contribute their time to the
development of \astropy projects.
We would like acknowledge the support of the Space Telescope Science Institute,
Harvard--Smithsonian Center for Astrophysics, and the South African Astronomical
Observatory.

Supported by the international Gemini Observatory, a program of NSF's NOIRLab,
which is managed by the Association of Universities for Research in Astronomy
(AURA) under a cooperative agreement with the National Science Foundation, on
behalf of the Gemini partnership of Argentina, Brazil, Canada, Chile, the
Republic of Korea, and the United States of America.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython}.
          % \package{photutils} \citep{photutils},
          % \package{specutils} \citep{specutils},
          % \package{regions} \citep{regions},
          % \package{gwcs} \citep{gwcs},
          % \package{synphot} \citep{synphot},
          % \package{ASDF} \citep{ASDF}.
          % \package{SOFA} \citep{sofa},
          % \package{ERFA} (\citealt{erfa})
          }

>>>>

@@

We acknowledge the Gordon and Betty Moore foundation for their continued
financial support.
This work is partially supported by NASA under Grant No. 80NSSC22K0347 issued
through the NASA ROSES program.
This work is partially supported by the international Gemini Observatory, a
program of NSF's NOIRLab, which is managed by the Association of Universities
for Research in Astronomy (AURA) under a cooperative agreement with the National
Science Foundation, on behalf of the Gemini partnership of Argentina, Brazil,
Canada, Chile, the Republic of Korea, and the United States of America.
We also thank NumFOCUS and the Python Software Foundation for financial
support.

The \astropy community is supported by and makes use of a number of
organizations and services outside the traditional academic community.
We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors.
Within the academic community, we thank institutions that make it possible that
astronomers and other developers on their staff can contribute their time to the
development of \astropy projects.
We would like acknowledge the support of the Space Telescope Science Institute,
Harvard--Smithsonian Center for Astrophysics, and the South African Astronomical
Observatory.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython},
          \package{photutils} \citep{photutils},
          \package{specutils} \citep{specutils},
          \package{regions} \citep{regions},
          \package{gwcs} \citep{gwcs},
          \package{synphot} \citep{synphot},
          \package{ASDF} \citep{ASDF}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }
